% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Rodrigo Luger} \hfill
\textsf{\small rodluger@gmail.com, http://rodluger.github.io} \\[0.5ex]
Postdoctoral Researcher, University of Washington\\[0.5ex]

\cvheading{Education}
\begin{list}{}{\cvlist}
\item
PhD 2015, Department of Physics, New York University. Advisor: Hogg
\item
MSc 2010, Department of Physics, Queen's University, Canada. Advisor: Widrow
\item
BSc 2008, Department of Physics, McGill University, Canada.
\end{list}

\cvheading{Positions}
\begin{list}{}{\cvlist}
\item
Associate Research Scientist, Flatiron Institute, 2017--present.
\item
Sagan Postdoctoral Fellow, University of Washington, 2015--2017.
\end{list}

\ifdefined\withpubs
    \cvheading{Publications}
    \input{pubs_summary}

    \begin{list}{}{\cvlist}
    \input{pubs}
    \end{list}
    
\fi

\cvheading{Selected invited talks \& tutorials}
\begin{list}{}{\cvlist}

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, Canadian Institute of Theoretical Astrophysics.

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, University of Birmingham.

\end{list}

\cvheading{Popular open-source software}
\begin{list}{}{\cvlist}

\item {\bf emcee} ---
    MCMC sampling in Python. Popular in astronomy;
    the paper has 524 citations as of 2016-01-26.
    \url{dfm.io/emcee}

\item {\bf George} ---
    Blazingly fast Gaussian processes for regression. Implemented in C++ and
    Python bindings. Joint work with applied mathematicians at NYU.
    \url{dfm.io/george}

\end{list}

\cvheading{Honors}
\begin{list}{}{\cvlist}

\item Kavli Fellow, 2015.
\item Sagan Postdoctoral Fellowship, 2015--present.
\item James Arthur Graduate Fellowship, 2014.
\item Horizon Fellowship in the Natural \& Physical Sciences, 2012.
\item Henry M. MacCracken Fellowship, 2010.
\item NSERC Undergraduate Summer Research Award, 2007.

\end{list}

% \ifdefined\withpubs
%     \newpage
% \fi

\cvheading{Professional service \& activities}
\begin{list}{}{\cvlist}
\item MAST Users Group --- Member
\item American Astronomical Society --- Full Member
\item Active Referee ---
    AAS Journals,
    Journal of Statistical Software,
    Journal of Open Source Software
\end{list}

\end{document}
